\chapter{Introduction}

\section{Project Objectives}
The purpose of this project is the design and implementation of an embedded system based on the \textbf{Nucleo C031C6} microcontroller, with particular attention to the interaction between hardware components and firmware logic.  
The main goal is to properly configure the peripherals, manage asynchronous events through interrupts, and continuously acquire data using a polling mechanism.  

Specifically, the developed firmware is required to demonstrate the following functionalities:
\begin{itemize}
    \item real-time acquisition and management of an analog signal through \textbf{polling};
    \item handling of asynchronous digital events through an \textbf{interrupt} routine;
    \item clear and modular organization of the code using the STM32 \textbf{HAL} libraries;
    \item generation of an \textbf{analog graph} of the acquired data, including the \texttt{RAW}, \texttt{NOISE}, and \texttt{Moving Average (MA)} modes;
    \item generation of a \textbf{digital graph} of the data obtained through interrupts;
    \item playback of an \textbf{acoustic signal} during continuous analog signal detection.
\end{itemize}

\section{Context}
The project is based on the \texttt{microcontrollers} repository, available at \\
\href{https://github.com/eagletrt/recruiting-sw/tree/master/microcontrollers}{github.com/eagletrt/recruiting-sw}.  
It is an embedded application that simulates a real-time event acquisition and detection system, aiming to integrate analog and digital readings and verify their behavior through serial and graphical output.

Originally, the task required the use of a \textbf{Hall sensor} for both analog and digital readings. However, due to a malfunction of the component, the sensor was replaced with a \textbf{potentiometer} for the analog part and a \textbf{button} for interrupt generation and digital input.  
This replacement allowed the overall project logic to remain unchanged.

\section{Structure of the Report}
This document is organized as follows:
\begin{itemize}
    \item \textbf{Chapter~2} describes the project requirements, the hardware used, and the software environment adopted for development;
    \item \textbf{Chapter~3} details the implementation and structure of the firmware;
    \item \textbf{Chapter~4} analyzes the main issues encountered during development and the solutions implemented;
    \item \textbf{Chapter~5} presents the results obtained and possible future optimizations;
    \item \textbf{Chapter~6} provides final conclusions and reflections on the overall project experience.
\end{itemize}
